### 2018-06-04 Writing/Tables/Tab_pooledscenarios_test.tex
compiled tables

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Tue Mar 27 14:03:13 2018
\begin{table}[ht]
\centering
\begin{tabular}{llr|rl}
  \hline
metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
RF & maxi:mini & 0.573 & 356436.000 & \textbf{0} \\ 
   & maxi:rand & 0.873 & 287225.000 & \textbf{0} \\ 
   & mini:rand & 0.856 & 95841.500 & \textbf{0} \\ 
  Tr & maxi:mini & 0.614 & 358800.000 & \textbf{0} \\ 
   & maxi:rand & 0.908 & 288223.500 & \textbf{0} \\ 
   & mini:rand & 0.858 & 98507.500 & \textbf{0} \\ 
   \hline
\end{tabular}
\caption{Difference between the pooled scenarios. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correction)} 
\label{Tab_pooledscenarios_test}
\end{table}

>>>>

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Tue Mar 27 14:03:13 2018
\begin{table}[ht]
\centering
\begin{tabular}{llr|rl}
  \hline
metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
RF & maxi:mini & 0.573 & 356436.000 & \textbf{0} \\ 
   & maxi:rand & 0.873 & 287225.000 & \textbf{0} \\ 
   & mini:rand & 0.856 & 95841.500 & \textbf{0} \\ 
  Tr & maxi:mini & 0.614 & 358800.000 & \textbf{0} \\ 
   & maxi:rand & 0.908 & 288223.500 & \textbf{0} \\ 
   & mini:rand & 0.858 & 98507.500 & \textbf{0} \\ 
   \hline
\end{tabular}
\caption{Differences between the pooled scenarios. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correction).} 
\label{Tab_pooledscenarios_test}
\end{table}
